The Globular Cluster System of the Auriga Simulations

### 2019-03-04 AurigaGCS.tex
Should now be done with describing observations. Moving on to results. Also commented out list of papers to read in introduction.

\begin{itemize}
    \item \citet{2005MNRAS.364..367D}: ``The radial profile of the stellar halo
    and metal-poor globular clusters of the Milky Way suggest that these components 
    formed in rare early peaks above $2.5 \sigma$ at redshift above 10. ''

    \item \citet{2017MNRAS.465.3622R}: ``GCs among oldest astrophysical objects.
    GCs form in the early Universe in highest density peaks
    \citep[e.g.][]{2005MNRAS.364..367D, 2009ApJ...706L.192B}''

    \item ``Hence, they witness most of the formation and evolution processes
    of galaxies, and can be used to probe them'' \citep{2006ARA&A..44..193B}
\end{itemize}

\todo[inline]{Paragraph: scientific context / state of the field: briefly summarise
    previous work and references work of other groups}
\begin{itemize}
\item Origin of the Milky Way globular clusters \citep{2017MNRAS.465.3622R}
\item GCs in FIRE \citep{2018MNRAS.474.4232K}
\item EMOSAICS project \citep{2018MNRAS.475.4309P}
\item GC-DMhalo connection \citep{2017MNRAS.472.3120B}
\item Origin of GC bimodality? \citep{2018MNRAS.479..200F}
\item \textit{GAIA} DR2: GC kinematics \citep{2018A&A...616A..12G}
\item Dating GC Tidal Disruption \citep{2018ApJ...859L..13B}
\item GC in N-body simulation \citep{2018ApJ...861...69C}
\item (Role of GC mass evolution on stream properties \citep{2018MNRAS.474.2479B})
\item GC formation from dwarfs to giants \citep{2018MNRAS.480.2343C}
\item (GC contribution to EOR \citep{2018MNRAS.479..332B})
\item Early Universe supermassive star / GC formation \citep{2018MNRAS.478.2461G}
\item GC formation in cold filaments \citep{2018ApJ...861..148M}
\item GC formation in high-redshift dwarf galaxies \citep{2018MNRAS.477..480Z}
\item GCs in MW outer region \citep{2017arXiv170804542P}
\item Impact of the Cutoff of the Cluster Initial Mass Function \citep{2018arXiv181001888C}
\item Metallicity gradients in the globular cluster systems of early-type galaxies: in situ and accreted components \citep{2018MNRAS.479.4760F}
\item Globular clusters in M31, Local Group, and external galaxies \citep{2016IAUS..317..120L}
\item Globular Clusters Formed within Dark Halos I: present-day abundance, distribution and kinematics \citep{2019MNRAS.482..219C}
\item (The mass of the Milky Way from satellite dynamics \citep{2018arXiv180810456C})
\item Globular cluster formation and evolution in the context of cosmological galaxy assembly: open questions \citep{2018RSPSA.47470616F}
\item The kinematics of globular clusters systems in the outer halos of the Aquarius simulations \citep{2016A&A...592A..55V}
\item Star Cluster Formation in Cosmological Simulations \citep{2017ApJ...834...69L, 2018ApJ...861..107L, 2018arXiv181011036L}
\item (A systematic analysis of star cluster disruption by tidal shocks - I. Controlled N-body simulations and a new theoretical model \citep{2018arXiv181200014W})
\item Spatial mixing of binary stars in multiple-population globular clusters \citep{2018MNRAS.tmp.3147H}
\item Star Clusters Across Cosmic Time \citep{2018arXiv181201615K}
\item Kinematics of Subclusters in Star Cluster Complexes: Imprint of their Parental Molecular Clouds \citep{2018arXiv181201858F}
\item Investigating the population of Galactic star formation regions and star clusters within a Wide-Fast-Deep Coverage of the Galactic Plane  \citep{2018arXiv181203025P}
\item Globular cluster number density profiles using \textit{Gaia} DR2 \citep{2019arXiv190108072D}
\item Clustering Clusters: unsupervised learning on GC observations (of log $M$,
    log $\sigma_0$, log $R_e$ , [Fe/H], log $|Z|$) to determine number of groups
    $k=2$ (disk/halo) or $k=3$ (disk/inner-halo/outer-halo): the optimal number
    of groups given the data is $k=3$. \citep{2019arXiv190105354P}.
\item There is a well-known hypothesis that Open Stars Clusters (OSCs) could form as a result
    of GCs crossing the disk. New kinematical data does not support
    this claim for two particular OSC-GC pairs, and does seem consistent
    with this scenario for six OSC-GC pairs \citep{2019arXiv190106481B}. (Note
    that GC crossing the disk could also trigger formation of multiple OSCs!)
\item DM halo mass can be inferred from number of globular cluster in galaxy 
    \citep{2019arXiv190100900B}
\item GCs in M31 outer halo \citep{2019arXiv190111229W}
% TODO: last checked arXiv Mar 2, 2019
\end{itemize}

\todo[inline]{Paragraph, narrowing open questions in GC research down to formation,
    possibly ``Bimodality suggests two formation mechanisms''. In-situ 
    formation vs. accretion in hierarchical build-up of galaxies naturally produces 
    two populations of globular cluster.}
\begin{itemize}
    \item ``colour bimodality, blue and red clusters \citep[e.g.][]{1985ApJ...293..424Z, 1999AJ....118.1526G, 2001AJ....121.2974L, 2006ApJ...639...95P}
    \item ``blue metal-poor (with distribution peaking at [Fe/H] $\approx -1.5$ for the Milky Way), no sign of rotation as a population (..) more metal-rich (peak at [Fe/H] $\approx -0.5$ in the Milky  Way) more spatially concentrated and rotating with the galaxy.'' \citep{1996AJ....112.1487H}
    \item ``Blue clusters from in early Universe in galaxies that merge later. In (wet) merger process starbursts generate red population \cite{1992ApJ...384...50A, 1987nngp.proc...18S}''
    \item ``\citet{1997AJ....113.1652F} propose instead that blue globulars form when the protogalaxy itself collapses, in a metal-poor and turbulence media. The red population would form later, once the galactic disc has settled. The formation of globular clusters would then be a multiphase process, with the first phase being interrupted possibly by cosmic reionization \citep{2002MNRAS.333..383B}.''
    \item ``\citet{2005ApJ...623..650K, 2014ApJ...796...10L} advocate
that major mergers are at the origin of both sub-populations: blue
clusters form during early mergers (z > 4) while the red ones appear
in mergers at lower redshifts (even after z = 1). Although, this
scenario, combined with star formation enhancement in mergers,
seems appropriate in dense galactic environment leading to the
assembly of massive elliptical galaxies, like in the Virgo Cluster
as tested by \citet{2014ApJ...796...10L}, it does not apply to Milky Way-
like systems where no recent major merger took place (Wyse 2001;
Deason et al. 2013; Ruchti et al. 2014, 2015).
\item ``\citet{1998ApJ...501..554C} argue that red clusters form in situ while the blue ones are accreted, either via merging satellite galaxies, or by tidal capture of the clusters themselves \citep[see also][]{2013ApJ...762...39T}.''
\end{itemize}

\todo[inline]{Paragraph: narrow the scientific motivation down to the scope of 
    this particular work}
\begin{itemize}
    \item The star formation model implemented in the Auriga simulations is capable of producing a suite/population of realistic Milky Way-like galaxies at redshift zero.
    \item (However) State of the art simulations still face numerical restrictions that requires a subgrid approach to star formation and feedback because individual stars (and their evolution) cannot yet be accounted for. Star formation thus occurs in a heuristic/probabilistic fashion for gas cells that fulfill some star formation criterion. The star particles enrich the gas with metals and energy, both according to pre-defined/pre-calculated yields for specific feedback processes (supernova type I and II, strong stellar winds of asymptotic giant branch stars, ). In addition, black holes are seeded in eligible haloes to account for feedback associated with an active galactic nucleus.
    \item The end-result of the star formation model is the production of simulated Milky Way-like galaxies. Therefore the question naturally arises whether or not the Auriga simulations are also capable of faithfully producing a globular cluster population as observed in the Milky Way.
    \item Globular cluster formation in cosmological zoom simulations is very interesting for two reasons. First of all, extragalactic observations typically show the integrated properties of globular clusters rather than that of the individual stars within the clusters. Moreover, the typical mass scale of globular clusters is comparable to the numerical (mass) resolution of cosmological zoom simulations. The detailed small scale physics that is at play for real world globular clusters appears in observations as the combined effect of the $10^{3-6}$ M\Sun, compared to a mass resolution of $10^{3-5}$ M\Sun for the Auriga simulations. Globular clusters can therefore serve as an ultimate test to the star formation model that is implemented in the numerical simulations. Secondly, cosmological zoom simulations provide an accurate recording of the full and detailed merger history of the simulated galaxy. This is important because theoretical paradigms for globular cluster formation in the literature know two distinct classes of GCs that are separated by their exact formation sites: an in-situ versus an accreted population. Cosmological zoom simulations uniquely allow for an investigation into globular cluster formation with particular focus on the in-situ and accreted populations.
\end{itemize}

@@

\section{Relevant observational data}
\label{sec:observations}
We summarise relevant observations of the globular cluster system of the Milky 
Way in Sec.~\ref{sec:milkyway}, and of Andromeda (M31) in Sec.~\ref{sec:andromeda}.
In the remainder of the paper we compare observed (integrated) globular cluster
properties to the Auriga simulations.

\subsection{Milky Way}
\label{sec:milkyway}
\citet[][2010 edition; hereafter H96e10]{1996AJ....112.1487H} provides a
catalogue of the Milky Way globular cluster system that contains properties of 
157 GCs. The authors initially estimated the size of the MW GCS to be 180~$\pm$~10,
thus, their catalogue to be $\sim$85\% complete. However, an additional 59 GCs 
have since been discovered by various authors. The total confirmed number of GCs 
in the MW adds up to 216 with new estimates now anticipating an additional thirty 
GCs yet to be discovered \citep[e.g.][and references therein]{2018ApJ...863L..38R}.

\citet{2019AJ....157...12B} communicate the latest efforts to aggregate the
available data, presented in their CatClu catalog. Amongst 10978 star clusters 
and alike objects in the Milky Way, the catalog contains 200 GCs and 94 GC 
candidates. Unfortunately a machine readable version of the catalog is unavailable
at this point in time. Therefore we utilise the H96e10 dataset nonetheless, but
we caution that the Harris catalogue is now believed to be (only) 53-72\% complete.

The relevant data fields that we use from H96e10 are the metallicity [Fe/H], the
Galactic distance components $X$, $Y$, and $Z$ (in kpc)\footnote{In a Sun-centered 
coordinate system: $X$ points toward Galactic center, $Y$ in direction of 
Galactic rotation, and $Z$ toward the North Galactic Pole. We calculate the 
galactocentric radius $R_{\text{GC}}=\sqrt{(X-R_\odot)^2 + Y^2 + Z^2}$, 
assuming the solar radius $R_\odot=8$~kpc.}, and absolute 
magnitude in the V-band $M_V$. We use the latter to calculate mass-estimates by 
assuming $M_{V,\odot}=4.83$ and a mass to light ratio $M/L_V = 1.7$~M/L$_{\odot}$, 
the mean for MW clusters \citep{2005ApJS..161..304M}.

@@

\subsection{Andromeda}
\label{sec:andromeda}
The fifth revision of the revised bologna catalogue (RBC~5, last updated 
August, 2012) is the latest edition of three decades of systematically 
collecting integrated properties of the globular cluster system of the 
Andromeda galaxy \citep[][and references therein]{2004A&A...416..917G}. One
contribution to RBC~5 is the work by \citet[][hereafter C11]{2011AJ....141...61C}. 
C11 delivers a uniform set of spectroscopic observations $316$ out of the 
$339$ GCs in the inner $1^\circ.6 (\sim 21)$~kpc, calibrated using the Milky 
Way GCS.

Globular clusters in the outer halo of M31, up to projected radii 
$R_{\text{proj}}\sim150$~kpc, are observed in the Pan-Andromeda Archaeological 
Survey \citep[PAndAS, ][hereafter H14]{2014MNRAS.442.2165H}, see also
\citet{2014MNRAS.442.2929V, 2019MNRAS.484.1756M}. H14 presents the
discovery of 59 new GCs and publishes updates to RBC~5. The work of H14 is
incorporated in the latest version\footnote{dated 23 Sep 2015; retrieved
from \url{https://www.cfa.harvard.edu/oir/eg/m31clusters/M31_Hectospec.html}} 
of the C11 dataset. It seems that the 2015 edition of C11 is the most recent 
aggregated dataset M31's GCS and we will therefore use this troughout the 
remainder of this work.

The relevant fields in the C11 dataset are the age, metallicities, and 
absolute visual magnitude.
\todo[inline]{
TODO: paraphrase ``For M31 GC masses we combine the catalogues of Caldwell et al. (2011, using the 
given masses) and Huxor et al. (2014, again assuming $M/L_V = 1.7$~M/L$_{\odot}$, 
e.g. Strader, Caldwell \& Seth 2011).''
}

For M31 we find an age distribution with a mean value of 10.8$\pm 10.8$~Gyr and a 
dispersion of 2.3~Gyr. Furthermore, 27 GCs have age-estimates below 10~Gyr, and
the minimum age is 4.8~Gyr.

\begin{figure}
    \includegraphics[width=\columnwidth]{{MW_M31_Age_HistogramMassWeighted}.png}
    \caption{
        Mass-weighted age distribution of 55 GCs in the MW
        \citep[data from][]{2013ApJ...775..134V} and 87 GCs
        in M31 \citep[data from][]{2011AJ....141...61C}.
        \label{fig:MW-M31-age}
    }
\end{figure}

\begin{align}
\end{align}
where $(\alpha_1, \delta_1)$ are the right ascension and declination (in degrees,
We adopt the values 
$(\alpha_0, \delta_0) = (0^{\text{h}}42^{\text{m}}44.3^{\text{s}}, 
+41^{\circ}16'9")$\footnote{See \url{https://ned.ipac.caltech.edu/}} , and  $D_{\text{M31}} = 778$~kpc 
(TODO: reference).

% TODO: Deprojection, assuming all GCs lie in the plane of the sky, inclination 
% $12.5^{\circ}$

\section{Results}
\label{sec:results}
We define GC candidates in the Auriga simulations as all star particles older 
than $10$~Gyr. The mean age-estimate of the $55$ MW GCs in V13 is $11.9\pm0.1$~Gyr
with a dispersion of $0.8$~Gyr, and the age-estimate for only one observed GC is 
smaller than $10$~Gyr.

@@

In Sec.~\ref{sec:metallicity} we investigate the metallicity distribution of the
GC candidates, in Sec.~\ref{sec:radial} we show the distribution of galactocentric
radii of the globular cluster candidates within the Auriga simulations, and we 
combine both in Sec.~\ref{sec:FeHRgc}. We continue our analysis with an investigation
of the properties of the proto-galaxies at times of birth of the accreted globular 
cluster population in Sec.~\ref{sec:birth-properties-of-accreted-gc-candidates}

@@

\todo[inline]{
Look into Pandromeda survey. Star counts, very wide angle survey
}

@@

>>>>

% \begin{itemize}
%     \item \citet{2005MNRAS.364..367D}: ``The radial profile of the stellar halo
%     and metal-poor globular clusters of the Milky Way suggest that these components 
%     formed in rare early peaks above $2.5 \sigma$ at redshift above 10. ''
% 
%     \item \citet{2017MNRAS.465.3622R}: ``GCs among oldest astrophysical objects.
%     GCs form in the early Universe in highest density peaks
%     \citep[e.g.][]{2005MNRAS.364..367D, 2009ApJ...706L.192B}''
% 
%     \item ``Hence, they witness most of the formation and evolution processes
%     of galaxies, and can be used to probe them'' \citep{2006ARA&A..44..193B}
% \end{itemize}

\todo[inline]{Paragraph: scientific context / state of the field: briefly summarise
    previous work and references work of other groups}
% \begin{itemize}
% \item Origin of the Milky Way globular clusters \citep{2017MNRAS.465.3622R}
% \item GCs in FIRE \citep{2018MNRAS.474.4232K}
% \item EMOSAICS project \citep{2018MNRAS.475.4309P}
% \item GC-DMhalo connection \citep{2017MNRAS.472.3120B}
% \item Origin of GC bimodality? \citep{2018MNRAS.479..200F}
% \item \textit{GAIA} DR2: GC kinematics \citep{2018A&A...616A..12G}
% \item Dating GC Tidal Disruption \citep{2018ApJ...859L..13B}
% \item GC in N-body simulation \citep{2018ApJ...861...69C}
% \item (Role of GC mass evolution on stream properties \citep{2018MNRAS.474.2479B})
% \item GC formation from dwarfs to giants \citep{2018MNRAS.480.2343C}
% \item (GC contribution to EOR \citep{2018MNRAS.479..332B})
% \item Early Universe supermassive star / GC formation \citep{2018MNRAS.478.2461G}
% \item GC formation in cold filaments \citep{2018ApJ...861..148M}
% \item GC formation in high-redshift dwarf galaxies \citep{2018MNRAS.477..480Z}
% \item GCs in MW outer region \citep{2017arXiv170804542P}
% \item Impact of the Cutoff of the Cluster Initial Mass Function \citep{2018arXiv181001888C}
% \item Metallicity gradients in the globular cluster systems of early-type galaxies: in situ and accreted components \citep{2018MNRAS.479.4760F}
% \item Globular clusters in M31, Local Group, and external galaxies \citep{2016IAUS..317..120L}
% \item Globular Clusters Formed within Dark Halos I: present-day abundance, distribution and kinematics \citep{2019MNRAS.482..219C}
% \item (The mass of the Milky Way from satellite dynamics \citep{2018arXiv180810456C})
% \item Globular cluster formation and evolution in the context of cosmological galaxy assembly: open questions \citep{2018RSPSA.47470616F}
% \item The kinematics of globular clusters systems in the outer halos of the Aquarius simulations \citep{2016A&A...592A..55V}
% \item Star Cluster Formation in Cosmological Simulations \citep{2017ApJ...834...69L, 2018ApJ...861..107L, 2018arXiv181011036L}
% \item (A systematic analysis of star cluster disruption by tidal shocks - I. Controlled N-body simulations and a new theoretical model \citep{2018arXiv181200014W})
% \item Spatial mixing of binary stars in multiple-population globular clusters \citep{2018MNRAS.tmp.3147H}
% \item Star Clusters Across Cosmic Time \citep{2018arXiv181201615K}
% \item Kinematics of Subclusters in Star Cluster Complexes: Imprint of their Parental Molecular Clouds \citep{2018arXiv181201858F}
% \item Investigating the population of Galactic star formation regions and star clusters within a Wide-Fast-Deep Coverage of the Galactic Plane  \citep{2018arXiv181203025P}
% \item Globular cluster number density profiles using \textit{Gaia} DR2 \citep{2019arXiv190108072D}
% \item Clustering Clusters: unsupervised learning on GC observations (of log $M$,
%     log $\sigma_0$, log $R_e$ , [Fe/H], log $|Z|$) to determine number of groups
%     $k=2$ (disk/halo) or $k=3$ (disk/inner-halo/outer-halo): the optimal number
%     of groups given the data is $k=3$. \citep{2019arXiv190105354P}.
% \item There is a well-known hypothesis that Open Stars Clusters (OSCs) could form as a result
%     of GCs crossing the disk. New kinematical data does not support
%     this claim for two particular OSC-GC pairs, and does seem consistent
%     with this scenario for six OSC-GC pairs \citep{2019arXiv190106481B}. (Note
%     that GC crossing the disk could also trigger formation of multiple OSCs!)
% \item DM halo mass can be inferred from number of globular cluster in galaxy 
%     \citep{2019arXiv190100900B}
% \item GCs in M31 outer halo \citep{2019arXiv190111229W}
% % TODO: last checked arXiv Mar 2, 2019
% \end{itemize}

\todo[inline]{Paragraph, narrowing open questions in GC research down to formation,
    possibly ``Bimodality suggests two formation mechanisms''. In-situ 
    formation vs. accretion in hierarchical build-up of galaxies naturally produces 
    two populations of globular cluster.}
% \begin{itemize}
%     \item ``colour bimodality, blue and red clusters \citep[e.g.][]{1985ApJ...293..424Z, 1999AJ....118.1526G, 2001AJ....121.2974L, 2006ApJ...639...95P}
%     \item ``blue metal-poor (with distribution peaking at [Fe/H] $\approx -1.5$ for the Milky Way), no sign of rotation as a population (..) more metal-rich (peak at [Fe/H] $\approx -0.5$ in the Milky  Way) more spatially concentrated and rotating with the galaxy.'' \citep{1996AJ....112.1487H}
%     \item ``Blue clusters from in early Universe in galaxies that merge later. In (wet) merger process starbursts generate red population \cite{1992ApJ...384...50A, 1987nngp.proc...18S}''
%     \item ``\citet{1997AJ....113.1652F} propose instead that blue globulars form when the protogalaxy itself collapses, in a metal-poor and turbulence media. The red population would form later, once the galactic disc has settled. The formation of globular clusters would then be a multiphase process, with the first phase being interrupted possibly by cosmic reionization \citep{2002MNRAS.333..383B}.''
%     \item ``\citet{2005ApJ...623..650K, 2014ApJ...796...10L} advocate
% that major mergers are at the origin of both sub-populations: blue
% clusters form during early mergers (z > 4) while the red ones appear
% in mergers at lower redshifts (even after z = 1). Although, this
% scenario, combined with star formation enhancement in mergers,
% seems appropriate in dense galactic environment leading to the
% assembly of massive elliptical galaxies, like in the Virgo Cluster
% as tested by \citet{2014ApJ...796...10L}, it does not apply to Milky Way-
% like systems where no recent major merger took place (Wyse 2001;
% Deason et al. 2013; Ruchti et al. 2014, 2015).
% \item ``\citet{1998ApJ...501..554C} argue that red clusters form in situ while the blue ones are accreted, either via merging satellite galaxies, or by tidal capture of the clusters themselves \citep[see also][]{2013ApJ...762...39T}.''
% \end{itemize}

\todo[inline]{Paragraph: narrow the scientific motivation down to the scope of 
    this particular work}
\begin{itemize}
    \item The star formation model implemented in the Auriga simulations is capable of producing a suite/population of realistic Milky Way-like galaxies at redshift zero.
    \item Therefore the question naturally arises whether or not the Auriga simulations are also capable of faithfully producing a globular cluster population as observed in the Milky Way (or Andromeda).
    \item Globular cluster formation in cosmological zoom simulations is very interesting for two reasons. First of all, extragalactic observations typically show the integrated properties of globular clusters rather than that of the individual stars within the clusters. Moreover, the typical mass scale of globular clusters is comparable to the numerical (mass) resolution of cosmological zoom simulations. The detailed small scale physics that is at play for real world globular clusters appears in observations as the combined effect of the $10^{3-6}$ M\Sun, compared to a mass resolution of $10^{3-5}$ M\Sun for the Auriga simulations. Globular clusters can therefore serve as an ultimate test to the star formation model that is implemented in the numerical simulations. Secondly, cosmological zoom simulations provide an accurate recording of the full and detailed merger history of the simulated galaxy. This is important because theoretical paradigms for globular cluster formation in the literature know two distinct classes of GCs that are separated by their exact formation sites: an in-situ versus an accreted population. Cosmological zoom simulations uniquely allow for an investigation into globular cluster formation with particular focus on the in-situ and accreted populations.
\end{itemize}

@@

\section{Relevant observational data}
\label{sec:observations}
We summarise relevant observations of the globular cluster system of the Milky 
Way in Sec.~\ref{sec:milkyway}, and of Andromeda (M31) in Sec.~\ref{sec:andromeda}.

\subsection{Milky Way}
\label{sec:milkyway}
\citet[][2010 edition; hereafter H96e10]{1996AJ....112.1487H} provides a
catalogue\footnote{See \url{https://www.physics.mcmaster.ca/Fac_Harris/mwgc.dat}} 
of the Milky Way globular cluster system that contains properties of 
157 GCs. The authors initially estimated the size of the MW GCS to be 180~$\pm$~10,
thus, their catalogue to be $\sim$85\% complete. However, an additional 59 GCs 
have since been discovered by various authors. The total confirmed number of GCs 
in the MW adds up to 216 with new estimates now anticipating an additional thirty 
GCs yet to be discovered \citep[e.g.][and references therein]{2018ApJ...863L..38R}.

\citet{2019AJ....157...12B} communicate the latest efforts to aggregate the
available data, presented in their CatClu catalog. Amongst 10978 star clusters 
and alike objects in the Milky Way, the catalog contains 200 GCs and 94 GC 
candidates. The CatClu catalog contains reference papers, positions, distances,
and total absolute V magnitude. Therefore we rely on the H96e10 dataset for all
other quantities, but we caution that the Harris catalogue is now believed to be (only) 53-72\% complete.

Specifically, the relevant data fields that we use from H96e10 are the 
metallicity [Fe/H], the Galactic distance components $X$, $Y$, and $Z$ (in 
kpc)\footnote{In a Sun-centered coordinate system: $X$ points toward Galactic 
center, $Y$ in direction of Galactic rotation, and $Z$ toward the North Galactic 
Pole. We calculate the galactocentric radius $R_{\text{GC}}=\sqrt{(X-R_\odot)^2
+ Y^2 + Z^2}$, assuming the solar radius $R_\odot=8$~kpc.}, and absolute 
magnitude in the V-band $M_V$. We use the latter to calculate mass-estimates by 
assuming $M_{V,\odot}=4.83$ and a mass to light ratio $M/L_V = 1.7$~M/L$_{\odot}$, 
the mean for MW clusters \citep{2005ApJS..161..304M}.

@@

\subsection{Andromeda}
\label{sec:andromeda}
The fifth revision of the revised bologna catalogue (RBC~5, last updated 
August, 2012) is the latest edition of three decades of systematically 
collecting integrated properties of the globular cluster system of the 
Andromeda galaxy \citep[][and references therein]{2004A&A...416..917G}. One
contribution to RBC~5 is the work by \citet[][hereafter C11]{2011AJ....141...61C},
subsequently updated by \citet[][hereafter CR16]{2016ApJ...824...42C}.

C11 and CR16 present a uniform set of spectroscopic observations calibrated 
on the Milky Way GCS of the inner $1.6^\circ~(\sim21)$~kpc that 
is believed to be 94\% complete. GCs in the outer stellar halo, up to 
$R_{\text{proj}}\sim150$~kpc, are observed in the Pan-Andromeda Archaeological
Survey \citep[PAndAS, ][hereafter H14]{2014MNRAS.442.2165H}, but see also
\citet{2014MNRAS.442.2929V} and \citet{2019MNRAS.484.1756M}. H14 presents the
discovery of 59 new GCs and publishes updates to RBC~5. The work of H14 is
incorporated in the latest public release\footnote{Last revised 23 Sep 2015, see
\url{https://www.cfa.harvard.edu/oir/eg/m31clusters/M31_Hectospec.html}} 
of the C11 dataset, further revised by CR16. It seems that CR16 is the most 
recent aggregated dataset of M31's GCS that contains properties of interest
for our study as it contains GCs in the inner region and in the outer halo. The 
relevant fields in the CR16 dataset that we use are the age, metallicity, and the 
mass-estimate\footnote{The authors assumed $M/L_V = 2$ (independent of [Fe/H])}.

% \todo[inline]{
% ``For M31 GC masses we combine the catalogues of Caldwell et al. (2011, using the 
% given masses) and Huxor et al. (2014, again assuming $M/L_V = 1.7$~M/L$_{\odot}$, 
% e.g. Strader, Caldwell \& Seth 2011).''
% }

\subsubsection*{Age estimates}
For M31 we find an age distribution with a mean value of 10.8$\pm 10.8$~Gyr and a 
dispersion of 2.3~Gyr. Furthermore, 27 GCs have age-estimates below 10~Gyr, and
the minimum age is 4.8~Gyr.

We present a mass-weighted histogram of the age-estimates of the 55 MW GCs in V13
and 85 GCs in M31 for which age-estimates are available in CR16, see 
Fig.~\ref{fig:MW-M31-age}.

\begin{figure}
    \includegraphics[width=\columnwidth]{{MW_M31_Age_HistogramMassWeighted}.png}
    \caption{
        Mass-weighted age distribution of 55 GCs in the MW
        \citep[data from][]{2013ApJ...775..134V} and 85 GCs
        in M31 \citep[data from][]{2016ApJ...824...42C}.
        \label{fig:MW-M31-age}
    }
\end{figure}

\subsubsection*{Calculation of galactocentric radius}
The projected galacocentric radius $R_{\text{proj}}$ is calculated following
\citet[][Sec.~4.1, eq.~4]{2019arXiv190111229W}. Specifically,
\begin{align}
    X &= A \sin{(\text{PA})} + B \cos{(\text{PA})} \nonumber \quad \text{and} \\
    Y &= - A \cos{(\text{PA})} + B \sin{(\text{PA})} \text{,}
\end{align}
where $A = \sin{(\alpha - \alpha_0)} \cos{\delta}$ and
$B = \sin\delta \cos\delta_0 - \cos{(\alpha - \alpha_0)} \cos\delta \sin\delta_0$
for the right ascension $\alpha$ (hourangle) and declination $\delta$ (degree) 
of the GCs. For the central position of M31 we take the preferred position 
from the NASA Extragalactic Database\footnote{\url{https://ned.ipac.caltech.edu/}}
entry of M31: $(\alpha_0, \, \delta_0) = 
(0^{\text{h}}42^{\text{m}}44.35^{\text{s}}, \, +41^{\circ}16'08.63")$.
The projected galactocentrid radius is calculated as $R_\text{proj} = 
\sqrt{X^2 + Y^2}$ (for $X$ and $Y$ in arcsec), and using the small angle 
approximation with a distance of $D_{\text{M31}} = 778$~kpc to convert to kpc.
TODO: McConnachie et al. 2005; Conn  et  al. 2012. Finally, we convert the 
projected distance ($R_{\text{proj}}$) to an `average deprojected distance` 
via the relationship $R_{\text{GC}} = R_{\text{proj}} \times (4/\pi)$.

\section{Results}
\label{sec:results}
We define GC candidates in the Auriga simulations as all star particles older 
than $10$~Gyr based on the age distribution of the MW GCS in 
Fig.~\ref{fig:MW-M31-age} and following \citet{2017MNRAS.465.3622R}.

@@

In Sec.~\ref{sec:metallicity} we investigate the metallicity distribution of the
GC candidates, in Sec.~\ref{sec:radial} we show the distribution of galactocentric
radii of the globular cluster candidates within the Auriga simulations, and we 
combine both in Sec.~\ref{sec:FeHRgc}. 
% We continue our analysis with an investigation
% of the properties of the proto-galaxies at times of birth of the accreted globular 
% cluster population in Sec.~\ref{sec:birth-properties-of-accreted-gc-candidates}

@@

@@

\todo[inline]{
\citet{2016ApJ...824...42C} writes:
``there are two broad, well-established differences:
(1) the M31 GC system is more populous than the MW system, by a factor of
$\sim$2-3, and (2) it does not exhibit the same obvious bimodality in
metallicity \citep{2000AJ....119..727B, 2009A&A...508.1285G, 2011AJ....141...61C, 
2013A&A...549A..60C}. Both of these aspects may be reflections of dramatic 
differences discovered in these galaxies stellar halos, where the M31 halo 
appears much more metal-enriched, with massive substructures suggesting a more 
active satellite accretion history \citep[e.g.][]{2009Natur.461...66M}''
}
